```{r reprex-options, include = FALSE}
options(
  keep.source = TRUE,
  rlang_trace_top_env = globalenv(),
  `rlang:::force_unhandled_error` = TRUE,
  rlang_backtrace_on_error = "full",
  crayon.enabled = FALSE,
  reprex.current_venue = "gh"
)
```

```{r, results = 'asis', echo = FALSE, include = file.exists('.Rprofile'), eval = file.exists('.Rprofile')}
cat(sprintf("*Local `.Rprofile` detected at `%s`*", normalizePath(".Rprofile")))
```

---
title: My manuscript
author: trinhdhk
date: "`r Sys.Date()`"
output: 
  reprex::reprex_document:
    advertise: no
    tidyverse_quiet: yes
    session_info: yes
knit: reprex::reprex_render
---

## What reprex provide
Describe your issue very briefly here. Then show it with a minimal, self-contained example in the following R chunk.

```{r}
x <- 1
y <- "2"
x + y
```

Inline code is working? `r x+1`
Plot will be automatically uploaded to imgur. Don't know whether it is good or bad thing?

```{r plot} 
plot(density(rnorm(1000, 0, 1)))
```


<details style="margin-bottom:10px;">
<summary>Session info</summary>
```{r }
sessionInfo()
```
</details>
